Title

### 2024-05-10 paper/main.tex
Updates

\begin{abstract}
	Constructing a Directed Acyclic Graph (DAG) from observational data,
	called causal discovery, is a fundamental problem in causal inference.
	Numerous algorithms have been developed to address it. However, their
	adoption in applied disciplines has been limited, possibly due to a
	lack of confidence in these algorithms stemming from them making
	obvious mistakes, and the difficulties in choosing the right algorithm
	for specific datasets. Consequently, in applied disciplines, these
	causal Directed Acyclic Graphs (DAGs) are predominantly constructed
	manually based on domain expertise. This makes it vital to test and
	potentially modify these models against data before using them for any
	analysis. Local testing based on Conditional Independence (CI) tests and
	effect sizes have been commonly used for this purpose. However,
	one of the current limitations of this approach is that there are no
	effect sizes for mixed data. To address this, we introduce a novel
	effect size measure for mixed data based on canonical correlations.
	This effect size is a generalization of some of the effect sizes used
	in special cases to mixed variables. Moreover, to assist researchers in
	constructing DAGs manually, we use the proposed mixed data effect size
	measure to build a web-based tool that can help researchers in
	constructing, validating, and modifying their DAGs with the help of
	available data. The tool iteratively suggests modifications to DAGs
	based on correlations that are not explained/over-explained by the DAG,
	while the expert chooses the direction of the edge between those
	variables. Empirically, we show that taking a greedy approach on the
	tool's recommendations can perform comparably to causal discovery
	algorithms, provided that the expert correctly determines the direction
	of the edges in at least one out of three cases, with performance
	improving as accuracy increases.
\end{abstract}

@@

\begin{algorithm}
	\caption{Expert Simulation}
	\While{True}{
	   $ e \gets \textnormal{Effects}(G) > \textnormal{THRESHOLD} $ \;
	   \If{$ \textnormal{len}(e) $}{
		   $ \textnormal{return}(G) $ \;
	   }
	   $ X, Y \gets \max_{X, Y} e $\;
	   $ dir \gets Expert(X, Y) $ \;
	}

>>>>

\begin{abstract}
	% Constructing a Directed Acyclic Graph (DAG) from observational data,
	% called causal discovery, is a fundamental problem in causal inference.
	% Numerous algorithms have been developed to address it. However, their
	% adoption in applied disciplines has been limited, possibly due to a
	% lack of confidence in these algorithms stemming from them making
	% obvious mistakes, and the difficulties in choosing the right algorithm
	% for specific datasets. Consequently, in applied disciplines, these
	% causal Directed Acyclic Graphs (DAGs) are predominantly constructed
	% manually based on domain expertise. This makes it vital to test and
	% potentially modify these models against data before using them for any
	% analysis. Local testing based on Conditional Independence (CI) tests and
	% effect sizes have been commonly used for this purpose. However,
	% one of the current limitations of this approach is that there are no
	% effect sizes for mixed data. To address this, we introduce a novel
	% effect size measure for mixed data based on canonical correlations.
	% This effect size is a generalization of some of the effect sizes used
	% in special cases to mixed variables. Moreover, to assist researchers in
	% constructing DAGs manually, we use the proposed mixed data effect size
	% measure to build a web-based tool that can help researchers in
	% constructing, validating, and modifying their DAGs with the help of
	% available data. The tool iteratively suggests modifications to DAGs
	% based on correlations that are not explained/over-explained by the DAG,
	% while the expert chooses the direction of the edge between those
	% variables. Empirically, we show that taking a greedy approach on the
	% tool's recommendations can perform comparably to causal discovery
	% algorithms, provided that the expert correctly determines the direction
	% of the edges in at least one out of three cases, with performance
	% improving as accuracy increases.

	Causal Discovery that is learning the causal graph from observational
	data is a fundamental problem in causal inference. The problem has been
	extensively studied and many algorithms have been developed to address
	it. However, their adaption in applied fields have been limited,
	possibly due to a lack of confidence in these algorithms stemming from
	them making obvious mistakes, and the difficulties in choosing the
	right algorithm for specific datasets. Moreover, these algorithms can
	usuallly only get us to markov equivance class where the remaining
	edges need to be somehow oriented before inference can be done from
	them. Consequently, in applied disciplines, these Directed Acyclic
	Graphs (DAGs) are predominantly constructed manually based on domain
	expertise. Due to being constructed by hand, testing these models is
	vital before making any inference using them. Local testing in these
	models can be done by checking whether the implied conditional
	independences (CIs) by the model hold in the data or not. (Shipley
	2000) also proposed a global test based on combining these local tests.
	Based on these local tests, in the case of continuous or discrete
	variables, we can start by modifying the worst offending test.
\end{abstract}

@@

\begin{algorithm}
	\caption{Expert Simulation}
	\While{True}{
	   $ e \gets \textnormal{Effects}(G) > \textnormal{THRESHOLD} $\;
	   $ e \gets e - \textnormal{blacklist} $\;
	   \If {$ e = 0 $}{
		$ G \gets G - e $ \;
		$ \textnormal{blacklist} \gets \textnormal{blacklist} \cup e $\;
	   } \;
	   \If{$ \textnormal{len}(e) = 0$}{
		   $ \textnormal{return}(G) $\;
	   }
	   $ X, Y \gets \max_{X, Y} e $\;
	   $ dir \gets Expert(X, Y, \alpha) $\;
	   $ G \gets G \cup dir $\;
	}
